---
title: FARS Vignette
author: "Adam Centurione"
date: "04/01/2020"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndex Entry{fars4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UFC-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#FARS Analysis with fars4
This package allows its useres to import .csv files of fatal car crash data and perform comparitive analysis and visualization of that data. Functions involved include:

make_filename(): to create a filename for the year(s) to be analyzed

fars_read(): to create a tibble from the dataframe imported from the .csv file

fars_read_years(): to reduce the data to the only the months which they occured and the number     of crashes, for the years being analyzed

fars_summarize_years(): to create a final summary table of the fars_read_years() outpute for      one or multiple years

fars_map_state(): to create a plot of all the fatal crashes which occured within a year for a specific state

For example:
##fars_summarize_years()
```{r echo= TRUE}
fars_summarize_years(2013:2015)
```

##fars_map_state()

State of Florida fatal crash locations for 2013:
```{r echo=FALSE}
fars_map_state(12, 2013)
```

While the final two functions are the most meaningful, the first three are mostly used to format the data into a manner which can be analyzed. 
